Week 1 Quiz
========================================================

## Question 1

The American Community Survey distributes downloadable data about United States communities. Download the 2006 microdata survey about housing for the state of Idaho using download.file() from here:

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06hid.csv

and load the data into R. The code book, describing the variable names is here:

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FPUMSDataDict06.pdf

How many housing units in this survey were worth more than $1,000,000?

1. 24
2. 53
3. 164
4. 31


```{r load data}

housingData = read.csv("getdata_data_ss06hid.csv")
str(housingData)
head(housingData)
# Val variable shows the property value... if we table it, number 24 represents values equal or above $1,000,000
table(housingData$VAL)

```

**ANS**: 53

## Question 2

Use the data you loaded from Question 1. Consider the variable FES in the code book. Which of the "tidy data" principles does this variable violate?

1. Tidy data has variable values that are internally consistent.
2. Tidy data has one observation per row.
3. Tidy data has one variable per column.
4. Each variable in a tidy data set has been transformed to be interpretable.


```{r Q2}
head(housingData$FES)
table(housingData$FES)
```

**ANS**:


## Question 3

Download the Excel spreadsheet on Natural Gas Aquisition Program here:

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FDATA.gov_NGAP.xlsx

Read rows 18-23 and columns 7-15 into R and assign the result to a variable called:

dat 

What is the value of:

sum(dat$Zip*dat$Ext,na.rm=T) 

(original data source: http://catalog.data.gov/dataset/natural-gas-acquisition-program)

1. 154339
2. 338924
3. 184585
4. 36534720

```{r Q3}
install.packages("xlsx")
library(xlsx)
dat = read.xlsx("getdata_data_DATA.gov_NGAP.xlsx",header=TRUE, sheetIndex=1,colIndex=7:15, rowIndex=18:23)
str(dat)
sum(dat$Zip*dat$Ext,na.rm=T)
```
**ANS**: 4


## Question 4

Read the XML data on Baltimore restaurants from here:

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Frestaurants.xml

How many restaurants have zipcode 21231?

1. 130
2. 156
3. 181
4. 127

```{r Q4}
install.packages("XML")
library(XML)
fileURL = "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Frestaurants.xml"
## xmlTreeParse function doesnt work so try downloading the xml file
doc = xmlTreeParse(fileURL)
download.file(fileURL, destfile= tf <- tempfile(fileext=".xml"))
doc = xmlParse(tf)
#extract zip
zip = xpathApply(doc, "/response/row/row/zipcode", xmlValue)
## add all the zips if they are equal to 21231
sum(zip == "21231")
```

**ANS**: 127


## Question 5

The American Community Survey distributes downloadable data about United States communities. Download the 2006 microdata survey about housing for the state of Idaho using download.file() from here:

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06pid.csv

using the fread() command load the data into an R object

DT 

Which of the following is the fastest way to calculate the average value of the variable

pwgtp15 

broken down by sex using the data.table package?

1. sapply(split(DT$pwgtp15,DT$SEX),mean)
2. mean(DT$pwgtp15,by=DT$SEX)
3. mean(DT[DT$SEX==1,]$pwgtp15); mean(DT[DT$SEX==2,]$pwgtp15)
4. tapply(DT$pwgtp15,DT$SEX,mean)
5. rowMeans(DT)[DT$SEX==1]; rowMeans(DT)[DT$SEX==2]
6. DT[,mean(pwgtp15),by=SEX]


```{r Q5}
fileURL = "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06pid.csv"
download.file(fileURL, destfile="DT.csv")
install.packages("data.table")
library(data.table)
DT = fread("DT.csv")
system.time(sapply(split(DT$pwgtp15,DT$SEX),mean))
system.time(mean(DT$pwgtp15,by=DT$SEX))
system.time(mean(DT[DT$SEX==1,]$pwgtp15)); system.time(mean(DT[DT$SEX==2,]$pwgtp15))
system.time(tapply(DT$pwgtp15,DT$SEX,mean))
system.time(rowMeans(DT)[DT$SEX==1]); system.time(rowMeans(DT)[DT$SEX==2])
system.time(DT[,mean(pwgtp15),by=SEX])
```

**ANS:** 1