Week 4 Quiz
========================================================

## Question 1

The American Community Survey distributes downloadable data about United States communities. Download the 2006 microdata survey about housing for the state of Idaho using download.file() from here:

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06hid.csv

and load the data into R. The code book, describing the variable names is here:

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FPUMSDataDict06.pdf

Apply strsplit() to split all the names of the data frame on the characters "wgtp". What is the value of the 123 element of the resulting list?

1. "wgtp"
2. "wgt" "15"
3. "15"
4. "" "15"


```{r load data}
# download file
download.file("https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06hid.csv", destfile="Quiz4_Q1.csv")
# download code book
download.file("https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FPUMSDataDict06.pdf", destfile="code_book_Quiz4_Q1.pdf")

#read data
communities = read.csv("Quiz4_Q1.csv")
str(communities)
strsplit(names(communities),"wgtp")

```

**ANS**: 4


## Question 2

Load the Gross Domestic Product data for the 190 ranked countries in this data set:

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FGDP.csv

Remove the commas from the GDP numbers in millions of dollars and average them. What is the average?

Original data sources: http://data.worldbank.org/data-catalog/GDP-ranking-table

1. 381668.9
2. 293700.3
3. 377652.4
4. 379596.5


```{r Q2}
install.packages("jpeg")
library(jpeg)

#download file
download.file("https://d396qusza40orc.cloudfront.net/getdata%2Fjeff.jpg",destfile="2Fjeff.jpg", mode="wb")

# read jpeg
img <- readJPEG("2Fjeff.jpg", native= TRUE)

#calculate quantiles, 30th and 80th quantiles
quantile(img, probs=c(.3,.8))

```

**ANS**: 3


## Question 3

Load the Gross Domestic Product data for the 190 ranked countries in this data set:

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FGDP.csv

Load the educational data from this data set:

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FEDSTATS_Country.csv

Match the data based on the country shortcode. How many of the IDs match? Sort the data frame in descending order by GDP rank (so United States is last). What is the 13th country in the resulting data frame?

Original data sources:
http://data.worldbank.org/data-catalog/GDP-ranking-table
http://data.worldbank.org/data-catalog/ed-stats

1. 190, Spain
2. 189, Spain
3. 234, St. Kitts and Nevis
4. 189, St. Kitts and Nevis
5. 190, St. Kitts and Nevis
6. 234, Spain


```{r Q3}
#download file
download.file("https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FGDP.csv",destfile="GDP_Data_Q3.csv")
download.file("https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FEDSTATS_Country.csv",destfile="educational_Data_Q3.csv")

#load data
gdp = read.csv("GDP_Data_Q3.csv",colClasses="character")
education = read.csv("educational_Data_Q3.csv",colClasses="character")

#structure
str(gdp)
str(education)

summary(gdp)
summary(education)

gdp$X
gdp$Gross.domestic.product.2012
education$CountryCode

# cleaned the data in the GDP to only include the 190 countries with a GDP rank.
gdp = subset(gdp, gdp$X != "" & gdp$Gross.domestic.product.2012 != "")

#Match the data based on the country shortcode. DO NOT INCLUDE ROW DATA IF NOT A MATCH
mergedData = merge(gdp, education, by.x="X", by.y="CountryCode", all=FALSE)

#structure
str(mergedData)
sum(is.na(mergedData$Gross.domestic.product.2012))
sum(is.na(mergedData$X))

#Order data by gdpRanks
mergedData <- mergedData[order(-as.numeric(mergedData$Gross.domestic.product.2012)) , ]
mergedData$Gross.domestic.product.2012
# check the country name
mergedData$Long.Name
mergedData$X.2

```
**ANS**: 4


## Question 4

What is the average GDP ranking for the "High income: OECD" and "High income: nonOECD" group?

1. 23, 30
2. 30, 37
3. 23, 45
4. 133.72973, 32.96667
5. 23.966667, 30.91304
6. 32.96667, 91.91304


```{r Q4}
sub_High_Income = subset(mergedData, mergedData$Income.Group == "High income: OECD" )
mean(as.numeric(sub_High_Income$Gross.domestic.product.2012))
sub_High_Income_non = subset(mergedData, mergedData$Income.Group == "High income: nonOECD" )
mean(as.numeric(sub_High_Income_non$Gross.domestic.product.2012))

```

**ANS**: 6


## Question 5

Cut the GDP ranking into 5 separate quantile groups. Make a table versus Income.Group. How many countries are Lower middle income but among the 38 nations with highest GDP?

1. 5
2. 12
3. 13
4. 1



```{r Q5}
install.packages("Hmisc")
library(Hmisc)
mergedData$RankingGroups = cut2(as.numeric(mergedData$Gross.domestic.product.2012), g=5 )
table(mergedData$RankingGroups, mergedData$Income.Group)
```

**ANS:** 1