Week 4 Quiz
========================================================

## Question 1

The American Community Survey distributes downloadable data about United States communities. Download the 2006 microdata survey about housing for the state of Idaho using download.file() from here:

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06hid.csv

and load the data into R. The code book, describing the variable names is here:

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FPUMSDataDict06.pdf

Apply strsplit() to split all the names of the data frame on the characters "wgtp". What is the value of the 123 element of the resulting list?

1. "wgtp"
2. "wgt" "15"
3. "15"
4. "" "15"


```{r load data}
# download file
download.file("https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06hid.csv", destfile="Quiz4_Q1.csv")
# download code book
download.file("https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FPUMSDataDict06.pdf", destfile="code_book_Quiz4_Q1.pdf")

#read data
communities = read.csv("Quiz4_Q1.csv")
str(communities)
testString = "This is a string"
strsplit(testString,"")
strsplit(names(communities),"wgtp")

```

**ANS**: 4


## Question 2

Load the Gross Domestic Product data for the 190 ranked countries in this data set:

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FGDP.csv

Remove the commas from the GDP numbers in millions of dollars and average them. What is the average?

Original data sources: http://data.worldbank.org/data-catalog/GDP-ranking-table

1. 381668.9
2. 293700.3
3. 377652.4
4. 379596.5


```{r Q2}

#download file
download.file("https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FGDP.csv",destfile="Quiz4_Q2.csv")

# read in data
gdp <- read.csv("Quiz4_Q2.csv")

names(gdp)

#190 ranked countries
gdp = subset(gdp, gdp$X != "" & gdp$Gross.domestic.product.2012 != "")

#gdp numbers in millions
gdp$X.3

## Remove Commas
removeCommas = gsub(",", "", gdp$X.3, fixed = TRUE)
mean(as.numeric(removeCommas))

```

**ANS**: 3


## Question 3

In the data set from Question 2 what is a regular expression that would allow you to count the number of countries whose name begins with "United"? Assume that the variable with the country names in it is named countryNames. How many countries begin with United? 

1. grep("*United",countryNames), 2
2. grep("*United",countryNames), 5
3. grep("^United",countryNames), 4
4. grep("^United",countryNames), 3 


```{r Q3}

grep("^United",gdp$X.2) #Begining of the line i.e. United at the start. Anything in the middle wouldn't match
grep("*United",gdp$X.2) 
grep("United$",gdp$X.2) #end of the line i.e. United at the end. Anything in the middle wouldn't match
grep("Un.ted",gdp$X.2) #Its gona look for Un followed by any possible character followed by ted.

```
**ANS**: 3


## Question 4

Load the Gross Domestic Product data for the 190 ranked countries in this data set:

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FGDP.csv

Load the educational data from this data set:

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FEDSTATS_Country.csv

Match the data based on the country shortcode. Of the countries for which the end of the fiscal year is available, how many end in June?

Original data sources:
http://data.worldbank.org/data-catalog/GDP-ranking-table
http://data.worldbank.org/data-catalog/ed-stats

1. 13
2. 15
3. 16
4. 8


```{r Q4}
download.file("https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FEDSTATS_Country.csv",destfile="Quiz4_Q4.csv")
education = read.csv("Quiz4_Q4.csv")
str(education)
gdp$X
education$CountryCode

#merge data
mergedData = merge(gdp, education, by.x="X", by.y="CountryCode", all=FALSE)

str(mergedData)


grep("^[Fiscal][Jj]une(.)", mergedData$Special.Notes)
mergedData$Special.Notes[95]

which(sapply(mergedData, function(x) any(grep("June",x))))
table(mergedData$Special.Notes)
```

**ANS**: 6


## Question 5

Cut the GDP ranking into 5 separate quantile groups. Make a table versus Income.Group. How many countries are Lower middle income but among the 38 nations with highest GDP?

1. 5
2. 12
3. 13
4. 1



```{r Q5}
install.packages("Hmisc")
library(Hmisc)
mergedData$RankingGroups = cut2(as.numeric(mergedData$Gross.domestic.product.2012), g=5 )
table(mergedData$RankingGroups, mergedData$Income.Group)
```

**ANS:** 1