Week 2 Quiz
========================================================

## Question 1

Register an application with the Github API here https://github.com/settings/applications. 
Access the API to get information on your instructors repositories (hint: this is the url you want "https://api.github.com/users/jtleek/repos"). 
Use this data to find the time that the datasharing repo was created. What time was it created? 
This tutorial may be useful (https://github.com/hadley/httr/blob/master/demo/oauth2-github.r). 
You may also need to run the code in the base R package and not R studio.

1. 2013-11-07T13:25:07Z
2. 2012-06-20T18:39:06Z
3. 2013-08-28T18:18:50Z
4. 2014-03-05T16:11:46Z



```{r load data}
install.packages("httpuv")
library(httpuv)
library(httr)
# 1. Find OAuth settings for github:
# http://developer.github.com/v3/oauth/
oauth_endpoints("github")

# 2. Register an application at https://github.com/settings/applications
# Insert your values below - if secret is omitted, it will look it up in
# the GITHUB_CONSUMER_SECRET environmental variable.
#
# Use http://localhost:1410 as the callback url
myapp <- oauth_app("github", "19dc655defc5726ea423", "eccb83db875b93387eae87a9399fa808d94bcea0")

# 3. Get OAuth credentials
github_token <- oauth2.0_token(oauth_endpoints("github"), myapp)
class(github_token)

# 4. Use API
req <- GET("https://api.github.com/users/jtleek/repos", config(token = github_token))
stop_for_status(req)
content(req)

# 5. Install JSONLITE package
install.packages("jsonlite")
library(jsonlite)

# 6. Now convert the contents into JSON format
json <- content(req)

json2 <- fromJSON(toJSON(json, pretty=TRUE))
class(json2)
str(json2)
names(json2)
cat(json2)

head(json2)
json2$owner$login

```

**ANS**: 1, To answer this question, you need to convert the JSON format to a dataframe and then simply use the head(json2) command and under the *created_at* variable/column you will find the answer

## Question 2

The sqldf package allows for execution of SQL commands on R data frames. We will use the sqldf package to practice the queries we might send with the dbSendQuery command in RMySQL. Download the American Community Survey data and load it into an R object called

 acs

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06pid.csv

Which of the following commands will select only the data for the probability weights pwgtp1 with ages less than 50?

1. sqldf("select * from acs where AGEP < 50 and pwgtp1")
2. sqldf("select pwgtp1 from acs where AGEP < 50")
3. sqldf("select * from acs")
4. sqldf("select * from acs where AGEP < 50") 

```{r Q2}
install.packages("sqldf")
library(sqldf)

# download file
download.file("https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06pid.csv", destfile="Quiz2_Q2.csv")

#load into R
acs = read.csv("Quiz2_Q2.csv")
str(acs)

#try queries
sqldf("select * from acs where AGEP <50 and pwgtp1")
sqldf("select pwgtp1 from acs where AGEP < 50") #this will select column pwgtp1 where agep is less than 50
sqldf("select * from acs") #this will select everything
sqldf("select * from acs where AGEP < 50") #this will select everything where age is less than 50
```

**ANS**: 2


## Question 3

Using the same data frame you created in the previous problem, what is the equivalent function to unique(acs$AGEP)

1. sqldf("select unique AGEP from acs")
2. sqldf("select distinct AGEP from acs")
3. sqldf("select distinct pwgtp1 from acs")
4. sqldf("select AGEP where unique from acs")


```{r Q3}
unique(acs$AGEP)
sqldf("select unique AGEP from acs") #not a SQL command
sqldf("select distinct AGEP from acs") #selects unique values from AGEP column in ACS dataframe
sqldf("select distinct pwgtp1 from acs") # selects unique values from pwgtp1 column in ACS dataframe
sqldf("select AGEP where unique from acs") #not a SQL command
```
**ANS**: 2


## Question 4

Read the XML data on Baltimore restaurants from here:

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Frestaurants.xml

How many restaurants have zipcode 21231?

1. 130
2. 156
3. 181
4. 127

```{r Q4}
install.packages("XML")
library(XML)
fileURL = "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Frestaurants.xml"
## xmlTreeParse function doesnt work so try downloading the xml file
doc = xmlTreeParse(fileURL)
download.file(fileURL, destfile= tf <- tempfile(fileext=".xml"))
doc = xmlParse(tf)
#extract zip
zip = xpathApply(doc, "/response/row/row/zipcode", xmlValue)
## add all the zips if they are equal to 21231
sum(zip == "21231")
```

**ANS**: 127


## Question 5

The American Community Survey distributes downloadable data about United States communities. Download the 2006 microdata survey about housing for the state of Idaho using download.file() from here:

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06pid.csv

using the fread() command load the data into an R object

DT 

Which of the following is the fastest way to calculate the average value of the variable

pwgtp15 

broken down by sex using the data.table package?

1. sapply(split(DT$pwgtp15,DT$SEX),mean)
2. mean(DT$pwgtp15,by=DT$SEX)
3. mean(DT[DT$SEX==1,]$pwgtp15); mean(DT[DT$SEX==2,]$pwgtp15)
4. tapply(DT$pwgtp15,DT$SEX,mean)
5. rowMeans(DT)[DT$SEX==1]; rowMeans(DT)[DT$SEX==2]
6. DT[,mean(pwgtp15),by=SEX]


```{r Q5}
fileURL = "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06pid.csv"
download.file(fileURL, destfile="DT.csv")
install.packages("data.table")
library(data.table)
DT = fread("DT.csv")
system.time(sapply(split(DT$pwgtp15,DT$SEX),mean))
system.time(mean(DT$pwgtp15,by=DT$SEX))
system.time(mean(DT[DT$SEX==1,]$pwgtp15)); system.time(mean(DT[DT$SEX==2,]$pwgtp15))
system.time(tapply(DT$pwgtp15,DT$SEX,mean))
system.time(rowMeans(DT)[DT$SEX==1]); system.time(rowMeans(DT)[DT$SEX==2])
system.time(DT[,mean(pwgtp15),by=SEX])
```

**ANS:** 1