Week 2 Quiz
========================================================

## Question 1

Register an application with the Github API here https://github.com/settings/applications. 
Access the API to get information on your instructors repositories (hint: this is the url you want "https://api.github.com/users/jtleek/repos"). 
Use this data to find the time that the datasharing repo was created. What time was it created? 
This tutorial may be useful (https://github.com/hadley/httr/blob/master/demo/oauth2-github.r). 
You may also need to run the code in the base R package and not R studio.

1. 2013-11-07T13:25:07Z
2. 2012-06-20T18:39:06Z
3. 2013-08-28T18:18:50Z
4. 2014-03-05T16:11:46Z



```{r load data}
install.packages("httpuv")
library(httpuv)
library(httr)
# 1. Find OAuth settings for github:
# http://developer.github.com/v3/oauth/
oauth_endpoints("github")

# 2. Register an application at https://github.com/settings/applications
# Insert your values below - if secret is omitted, it will look it up in
# the GITHUB_CONSUMER_SECRET environmental variable.
#
# Use http://localhost:1410 as the callback url
myapp <- oauth_app("github", "19dc655defc5726ea423", "eccb83db875b93387eae87a9399fa808d94bcea0")

# 3. Get OAuth credentials
github_token <- oauth2.0_token(oauth_endpoints("github"), myapp)

# 4. Use API
req <- GET("https://api.github.com/users/jtleek/repos", config(token = github_token))
stop_for_status(req)
content(req)

```

**ANS**: 53

## Question 2

Use the data you loaded from Question 1. Consider the variable FES in the code book. Which of the "tidy data" principles does this variable violate?

1. Tidy data has variable values that are internally consistent.
2. Tidy data has one observation per row.
3. Tidy data has one variable per column.
4. Each variable in a tidy data set has been transformed to be interpretable.


```{r Q2}
head(housingData$FES)
table(housingData$FES)
```

**ANS**:


## Question 3

Download the Excel spreadsheet on Natural Gas Aquisition Program here:

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FDATA.gov_NGAP.xlsx

Read rows 18-23 and columns 7-15 into R and assign the result to a variable called:

dat 

What is the value of:

sum(dat$Zip*dat$Ext,na.rm=T) 

(original data source: http://catalog.data.gov/dataset/natural-gas-acquisition-program)

1. 154339
2. 338924
3. 184585
4. 36534720

```{r Q3}
install.packages("xlsx")
library(xlsx)
dat = read.xlsx("getdata_data_DATA.gov_NGAP.xlsx",header=TRUE, sheetIndex=1,colIndex=7:15, rowIndex=18:23)
str(dat)
sum(dat$Zip*dat$Ext,na.rm=T)
```
**ANS**: 4


## Question 4

Read the XML data on Baltimore restaurants from here:

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Frestaurants.xml

How many restaurants have zipcode 21231?

1. 130
2. 156
3. 181
4. 127

```{r Q4}
install.packages("XML")
library(XML)
fileURL = "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Frestaurants.xml"
## xmlTreeParse function doesnt work so try downloading the xml file
doc = xmlTreeParse(fileURL)
download.file(fileURL, destfile= tf <- tempfile(fileext=".xml"))
doc = xmlParse(tf)
#extract zip
zip = xpathApply(doc, "/response/row/row/zipcode", xmlValue)
## add all the zips if they are equal to 21231
sum(zip == "21231")
```

**ANS**: 127


## Question 5

The American Community Survey distributes downloadable data about United States communities. Download the 2006 microdata survey about housing for the state of Idaho using download.file() from here:

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06pid.csv

using the fread() command load the data into an R object

DT 

Which of the following is the fastest way to calculate the average value of the variable

pwgtp15 

broken down by sex using the data.table package?

1. sapply(split(DT$pwgtp15,DT$SEX),mean)
2. mean(DT$pwgtp15,by=DT$SEX)
3. mean(DT[DT$SEX==1,]$pwgtp15); mean(DT[DT$SEX==2,]$pwgtp15)
4. tapply(DT$pwgtp15,DT$SEX,mean)
5. rowMeans(DT)[DT$SEX==1]; rowMeans(DT)[DT$SEX==2]
6. DT[,mean(pwgtp15),by=SEX]


```{r Q5}
fileURL = "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06pid.csv"
download.file(fileURL, destfile="DT.csv")
install.packages("data.table")
library(data.table)
DT = fread("DT.csv")
system.time(sapply(split(DT$pwgtp15,DT$SEX),mean))
system.time(mean(DT$pwgtp15,by=DT$SEX))
system.time(mean(DT[DT$SEX==1,]$pwgtp15)); system.time(mean(DT[DT$SEX==2,]$pwgtp15))
system.time(tapply(DT$pwgtp15,DT$SEX,mean))
system.time(rowMeans(DT)[DT$SEX==1]); system.time(rowMeans(DT)[DT$SEX==2])
system.time(DT[,mean(pwgtp15),by=SEX])
```

**ANS:** 1